---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# udiscr

[![Travis-CI Build Status](https://travis-ci.com/irudnyts/udiscr.svg?token=Spwopnmy37EZMsL4nDza&branch=master)](https://travis-ci.com/irudnyts/udiscr.svg?token=Spwopnmy37EZMsL4nDza&branch=master)

## Overview
A set of tools for generating a discrete approximation of
univariate continuous distributions. The list of methods includes
bracket-median, bracket-mean, extended Pearson-Tukey three point
approximation, extended Swanson-Megill.

## Instalation
The package is not (yet) submitted to CRAN, and is located in a private repository.
If one has an access to the github repo, it is possible to install the last 
development version:

```{r, eval=FALSE}
# install.packages("devtools")
# library("devtools")
devtools::install_github("irudnyts/udiscr")
```
